Semantic Prediction in {R}ussian

### 2020-04-11 paper.tex

As Kuperberg and Jaeger claim in their “What do we mean by prediction in language comprehension?” \cite{kuperberg-jaeger}, the reaction time is in direct proportion with the predictability of the word: the more predictable the word is the faster is the reaction. Moreover, predictability of a word or a context defines fixation time in eye-movement studies as a result of the language comprehension process. This implies that language comprehension must be predictive. The authors also state that as the previous context expands, the predictability of the next word increases leading to - in cloze tests - higher accuracy of predicting the next word, and - in eye-movement experiments - to shorter fixation duration.

The literature contains several different algorithms for cloze answer generation. In \cite{zhou-cloze} the authors state the importance of next word prediction in language modeling and its potential contribution to OCR and handwriting recognition. The authors enhance existing models with ELMo and BERT language models and train on the CLOTH dataset of cloze tests. BERT models show the highest performance (0.86 and 0.83 accuracy scores on test dataset for BERT Large and BERT Base respectively), as this model was initially trained to recover masked tokens in text. At the same time, the ELMo model's poor performance could be due to the lack of parameter tuning and the fact that ELMo was trained for the next sequence word prediction.

>>>>

As Kuperberg and Jaeger claim in their “What do we mean by prediction
in language comprehension?” \cite{kuperberg-jaeger}, the reaction time is in direct ratio with the predictability of the word: the more predictable the word is the faster is the reaction time. Moreover, predictability of a word or a context defines fixation time in eye-movement studies as a result of the language comprehension process. This implies that language comprehension must be predictive. The authors also state that as the previous context expands, the predictability of the next word increases leading to - in cloze tests - higher accuracy of predicting the next word, and - in eye-movement experiments - to shorter fixation duration.

Several scientific papers propose different algorithms for cloze answer generation. In \cite{zhou-cloze} the authors state the importance of next word prediction in language modeling and its potential contribution to OCR and handwriting recognition. The authors enhance existing models with ELMo and BERT language models and train on the CLOTH dataset of cloze tests. Expectedly, BERT models show the highest performance (0.86 and 0.83 accuracy scores on test dataset for BERT Large and BERT Base respectively), as this model was initially trained to recover masked tokens in text. At the same time, ELMo model's poor performance could be due to the lack of parameter tuning and the fact that ELMo was trained for the next sequence word prediction.
